Software Citation Principles

### 2016-04-17 sc-principles/software-citation-principles.tex
Clarified metadata for use case data are basic/minimal.
Closes issue #123. Also removed some old comments.

\newcommand*\rot[1]{\begin{turn}{90} #1 \end{turn}}%
\rowcolors{4}{gray!25}{white}
\begin{table}[tbhp]
\caption{Use cases for software citation, adapted from~\cite{SC-Use-Cases}.}
%``Researcher'' includes both academic researchers (e.g., postdoc, tenure-track
%faculty member) and research software engineers;
%``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software;
%``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility;
%examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search;
%domain groups include bioCADDIE~\cite{bioCADDIE}, Computational Infrastructure for Geodynamics (CIG)~\cite{CIG}, etc.;
%``repository'' refers to public software repositories such as Astronomy Source Code Library (ASCL)~\cite{ascl},
%GitHub, Netlib, Comprehensive R Archive Network (CRAN), institutional repositories;
%``funder'' is a group that funds software or work using software; and
%``unique ID'' refers to identifiers such as a DOI, ARK, or PURL.
%}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c c@{}}
\toprule
 & & \multicolumn{9}{c}{Requirements} \\
 \cmidrule{3-11}
Stakeholder & wants to 	& \rot{Unique identifier} &  \rot{Software name} & \rot{Author(s)} & \rot{Contributor role} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Indexed citations} & \rot{Software license}  \\
\midrule
Researcher            & 1.\ use someone else's software for a paper      & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & 2.\ use someone else's software for new software & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 3.\ contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 4.\ find citations of software               & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Researcher            & 5.\ get credit for software development      & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 6.\ ``reproduce'' analysis                   & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 7.\ benchmark software                       & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 8.\ find software to implement task          & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet & \textbullet & \textbullet \\
Publisher             & 9.\ publish software paper                   & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             \\
Publisher             & 10.\ publish papers that cite software        & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Indexer               & 11.\ build catalog of software                & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet \\
Domain group\slash library\slash archive          & 12.\ build software catalog\slash registry                & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet &             &             \\
Repository            & 13.\ show scientific impact of holdings       & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Funder                & 14.\ show how funded software has been used   & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Evaluator             & 15.\ evaluate contributions of researcher     & \textbullet &             & \textbullet & \textbullet &             & \textbullet &             & \textbullet &             \\
Citation manager      & 16.\ store software entry        			 & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

>>>>

\newcommand*\rot[1]{\begin{turn}{90} #1 \end{turn}}%
\rowcolors{4}{gray!25}{white}
\begin{table}[tbhp]
\caption{Use cases and basic metadata requirements for software citation, adapted from~\cite{SC-Use-Cases}.}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c c@{}}
\toprule
 & & \multicolumn{9}{c}{Requirements} \\
 \cmidrule{3-11}
Stakeholder & wants to 	& \rot{Unique identifier} &  \rot{Software name} & \rot{Author(s)} & \rot{Contributor role} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Indexed citations} & \rot{Software license}  \\
\midrule
Researcher            & 1.\ use someone else's software for a paper      & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & 2.\ use someone else's software for new software & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 3.\ contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 4.\ find citations of software               & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Researcher            & 5.\ get credit for software development      & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 6.\ ``reproduce'' analysis                   & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 7.\ benchmark software                       & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 8.\ find software to implement task          & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet & \textbullet & \textbullet \\
Publisher             & 9.\ publish software paper                   & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             \\
Publisher             & 10.\ publish papers that cite software        & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Indexer               & 11.\ build catalog of software                & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet \\
Domain group\slash library\slash archive          & 12.\ build software catalog\slash registry                & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet &             &             \\
Repository            & 13.\ show scientific impact of holdings       & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Funder                & 14.\ show how funded software has been used   & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Evaluator             & 15.\ evaluate contributions of researcher     & \textbullet &             & \textbullet & \textbullet &             & \textbullet &             & \textbullet &             \\
Citation manager      & 16.\ store software entry        			 & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%
